---
title: "DATA 605 Assginment 7"
author: "Jun Pan"
date: "March 17, 2019"
output: html_document
---


```{r}
library(knitr)
```


1.  Let X1, X2, . . . , Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi's. Find the distribution of Y . 


$k^n$ = total number of options to assign the values to Xi

$(k???1)^n$  will represent the combinations where none of the Xi are equal to 1.

so: 
$P(X=1) = (k^n ??? (k ??? 1)^n)/k^n$

$P(x=2) = ((k ??? 2+ 1)^n ??? (k ??? 2)^n)/kn$

$P(X=3)  = ((k ??? 3 +1 )^n ??? (k ??? 3)^n)/k^n)$

```````````````
Therefore, the probability distribution of  can be represented as:
$P(X=m) = ((k???m+1)^n???(k???m)^n)/k^n$






2.  Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).  This machine has a manufacturer's expected lifetime of 10 years.  This means that we expect one failure every ten years.  (Include the probability statements and R Code for each part.). 

a.  What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a geometric.  (Hint: the probability is equivalent to not failing during the first 8 years..) 


```{r}
p = 1/10
q = 1-p
n <- 8
round(pgeom(8,p,lower.tail = F), 3)
```
The probability that the machine will fail after 8 years is 0.387.

Expected value: 1/p = 1/0.1 = 10 years(agrees with exepcted value in the problem description)
```{r}
#standard deviation
sqrt(q/p^2)
```



b.  What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as an exponential.   

```{r}
lambda <- 1/10
k = 8
exp(-lambda*k)
```
Probability is 0.449.

```{r}
1/lambda#expected value
```

```{r}
sqrt(1/lambda^2)#standard deviation
```



c.  What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a binomial.  (Hint:  0 success in 8 years)   

```{r}
#probabiliy of fail after yr8
n <- 8
p <- 1/10
q <- 1-p
k <- 0

dbinom(k, n, p)
```

```{r}
#expected value
n*p
```

```{r}
#standard deviaion
sqrt(n*p*q)
```



d.  What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a Poisson.   
 
```{r}
#probability
lambda <- 8/10
ppois(0, lambda = 0.8)
```
 
Expected value 0.8

```{r}
#standard deviation
sqrt(0.8)
```

 
 




